---
title: "Example of potentially valid mapping extent"
author: "Thomas Nauss"
output:
  html_document:
    df_print: paged
---

The following illustrates the potential spatial prediction extent for an 
arbitrarily choosen Sentinel-2 satellite scene.

```{r, echo = FALSE, warning = FALSE, message = FALSE}
# Set up working environment and defaults --------------------------------------
library(envimaR)
root_folder = path.expand("~/plygrnd/Kili-SES/")
source(file.path(root_folder, "Kili-SES-Playground/src/functions/000_setup.R"))
```


```{r, eval = FALSE, echo = FALSE}
# Load data and extract value ranges for Kili-SES observation plots ------------
sen2files = list.files(envrmt$path_sentinel2, pattern = glob2rx("b*.tif"), 
                       full.names = TRUE)
sen2data = stack(sen2files)

plots = readOGR(file.path(envrmt$path_plots, "BPolygon.shp"), "BPolygon")

tdat_range = extract(sen2data, plots, df = TRUE)
saveRDS(tdat_range, file.path(envrmt$path_rds_data, "tdat_range.rds"))

tdat_range = melt(tdat_range, id.vars = "ID")

tdat_range$variable = factor(tdat_range$variable, 
                             levels = c("b2", "b3", "b4", "b5", "b6", "b7", "b8",
                                       "b8A", "b11", "b12"))


# Compile prediction extent maps -----------------------------------------------

valrastmaps = lapply(names(sen2data), function(l){
  minmaxval = minmax(tdat_range$value[tdat_range$variable == l])
  rastmap = mapvalid(sen2data[[l]], minmaxval)
  return(rastmap)
})
valrastmaps = stack(valrastmaps)
saveRDS(valrastmaps, file.path(envrmt$path_rds_data, "valrastmaps.rds"))

# valrastmaps_overlayed = overlay(valrastmaps, fun = mean)
# saveRDS(valrastmaps_overlayed, 
#         file.path(envrmt$path_rds_data, "valrastmaps_overlayed.rds"))

```


```{r, echo = FALSE}
# Set up working environment and defaults --------------------------------------
plots = readOGR(file.path(envrmt$path_plots, "BPolygon.shp"), "BPolygon")
tdat_range = readRDS(file.path(envrmt$path_rds_data, "tdat_range.rds"))
tdat_range = melt(tdat_range, id.vars = "ID")
valrastmaps = readRDS(file.path(envrmt$path_rds_data, "valrastmaps.rds"))
```


The figure illustrates the value range of the individual Sentinel-2 bands across all 65 study plots.
```{r, message = FALSE, warning = FALSE}
ggplot(tdat_range, aes(x=variable, y=value)) + 
  geom_violin(trim=FALSE, col = "red") + 
  labs(x = "Sentinel-2 bands", y = "Values")
```

The maps indicate the potential prediction area for each Sentinel-2 band. Black color indicates areas where the recorded spectral values are outside the range of recorded values within the 65 study plots. At least for those areas we have to assume that the prediction error of some variable of interest (e.g. diversity of an animal group) increases if the respective band is essential for the respective model. The actual mapping area is likely further reduced due to increasing errors in some other value ranges although they are covered within the study plots.

Use the layer buttons on the left to view the inidividual layers. As you can see, the valid extent is not the same for each band.

```{r, message = FALSE, warning = FALSE}
pal <- colorRampPalette(brewer.pal(9, "BrBG"))
mapview(valrastmaps, col.regions = pal(256), na.color = "black")

## create standalone .html
# mapshot(m, url = "mof_map.html")
```

